Video-Agnostic Perturbations: Efficient Targeted Attacks \\ for Siamese Visual Tracking

### 2021-01-14 博士/论文提交/adversarial_attack/IJCAI/FormattingGuidelines-IJCAI-21/main.tex
完善 introduction

Recently, the robustness of Siamese trackers have recently attracted a lot of attention \cite{TemporallyTransferablePerturbations} \cite{efficient} \cite{SPARK}. Despite the impressive performance of Siamese architectures on challenging visual object tracking task, these trackers were shown to be highly vulnerable to perturbations.
\cite{TemporallyTransferablePerturbations} \textcolor{black}{propose a framework to generate a single temporally transferable adversarial perturbation from the object template image only. This perturbation can then be added to every search image to adversarially attack the subsequent video frames.}
\cite{efficient} \textcolor{black}{present an end-to-end network FAN (Fast Attack Network) that uses a novel drift loss combined with the embedded feature loss to attack the Siamese network based trackers.}
\cite{SPARK} \textcolor{black}{propose the spatial-aware online incremental attack (a.k.a. SPARK) that performs spatial-temporal sparse incremental perturbations online and makes the adversarial attack less perceptible.}

All the above methods can fool object trackers successfully. However, these attack methods are not suitable for the real-world online-tracking phase where we can not get access to the limited computational resources.
The reason is, visual object tracking is a computationally intensive task which usually needs to be run in real time, but the computational source of small platforms (e.g., mobile, robotic, self-driving car) used to deploy the trackers is often limited.
Therefore, the attack approaches for object tracking should occupy as little computing resources as possible.
But the reality is that most attack algorithms either perform iterative optimisation to calculate adversarial examples, or generate perturbations through Generative Adversarial Networks which occupy the GPU memory.

@@

\textcolor{black}{Different from the existing attack methods which are intrinsic dependent on videos, we generate the perturbations that can fool the network on most natural videos. Perturbing a new target then only involves the mere addition/paste operation of the universal perturbations to the template/search image -- and does not require solving an optimisation problem/gradient computation.}
Overall, our contributions can be summarized as follows:
\begin{itemize}
\item We show the existence of universal video-agnostic perturbations for state-of-the-art deep Siamese trackers. To the best of our knowledge, this is the first work to perform universal targeted attack against the visual object tracking task.
\item We propose an end-to-end pipeline to generate the universal perturbations using large scale object tracking dataset.
\item Unlike most existing attack methods which only attack the classification branch of the tracker, we simultaneously manipulate the classification and bounding box regression result of the Siamese tracker.
\item Experiment results on OTB2015 \cite{OTB}, GOT-10k \cite{GOT-10k} and LaSOT \cite{GOT-10k} datasets demonstrate that our method can effectively fool the Siamese trackers in a targeted attack manner, which comes at virtually no cost.
\end{itemize}

>>>>

Recently, the robustness of Siamese trackers have recently attracted a lot of attention \cite{TemporallyTransferablePerturbations,efficient,SPARK}. Despite the impressive performance of Siamese architectures on challenging visual object tracking task, these trackers were shown to be highly vulnerable to perturbations.
\cite{TemporallyTransferablePerturbations} propose a framework to generate a single temporally transferable adversarial perturbation from the object template image only. This perturbation can then be added to every search image to adversarially attack the subsequent video frames.
\cite{efficient} present an end-to-end network FAN (Fast Attack Network) that uses a novel drift loss combined with the embedded feature loss to attack the Siamese network based trackers.
\cite{SPARK} propose the spatial-aware online incremental attack (a.k.a. SPARK) that performs spatial-temporal sparse incremental perturbations online and makes the adversarial attack less perceptible.

All the above methods can fool object trackers successfully. However, these attack methods are not suitable for the real-world online-tracking phase where we can not get access to the limited computational resources.
The reason is, visual object tracking is a computationally intensive task which usually needs to be run in real time, but the computational resources of small platforms (e.g., mobile, robotic, self-driving car) used to deploy the trackers are often limited.
Therefore, the attack approaches for object tracking should occupy as little computing resources as possible.
But the reality is that most attack algorithms either perform iterative optimisation to calculate adversarial examples, or generate perturbations through Generative Adversarial Networks which occupy the GPU memory.

@@

Different from the existing attack methods which are intrinsic dependent on videos, we generate the perturbations that can fool the network on most natural videos. Perturbing a new target then only involves the mere addition/paste operation of the universal perturbations to the template/search image -- and does not require solving an optimisation problem or network inference.
Overall, our contributions can be summarized as follows:
\begin{itemize}
\item We show the existence of universal video-agnostic perturbations for state-of-the-art deep Siamese trackers. To the best of our knowledge, this is the first work to perform universal targeted attack against the visual object tracking task.
\item We propose an end-to-end pipeline to generate the universal perturbations using large scale object tracking dataset.
\item Unlike most existing attack methods which only attack the classification branch of the tracker, we simultaneously manipulate the classification and bounding box regression result of the Siamese tracker.
\item Experiment results on OTB2015 \cite{OTB}, GOT-10k \cite{GOT-10k} and LaSOT \cite{GOT-10k} datasets demonstrate that our method can effectively fool the Siamese trackers in a targeted attack manner, which comes at virtually no cost.
\end{itemize}
